Did covid encourage assaults in Toronto neighbourhoods in 2020?

### 2022-04-27 outputs/paper/paper.Rmd
Completed paper, finished discussion and proofread. completed datasheet and knitted pdf

y= number of assaults in a neighbourhood,
x_1 = number of female covid cases in a neighbourhood,
x_2 = number of male covid cases in a neighbourhood,
x_3 = number of covid cases for people between ages 20 and 29
x_4 = number of covid cases for people between ages 30 and 39,
x_5 = number of covid cases for people between ages 40 and 49.

>>>>

y= number of assaults in a neighbourhood,
x_1 = number of female covid cases in a neighbourhood,
x_2 = number of male covid cases in a neighbourhood,
x_3 = number of covid cases for people between ages 20 and 29,
x_4 = number of covid cases for people between ages 30 and 39,
x_5 = number of covid cases for people between ages 40 and 49.
